The design flaw of npm and how `everything' broke it

### 2024-02-27 Paper/2/Paper.tex
Almost done?!

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that
  allows developers to share node packages and libraries \cite{npm}. This article will
  review and analyze the design flaw of npm and how it was broken by a single
  package, and will also review how GitHub responded to the incident and what
  actions they took in response.
\end{abstract}

@@

The npm registry is a critical piece of infrastructure for the entire JavaScript
community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
that the npm registry will be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
incident in 2023 \cite{youtube-everything} have shown that the npm registry is
not as mature as developers had hoped.

\section{Historical Background}
\subsection{Introduction}
One of the most infamous events in the history of npm was the left-pad incident.
Azer Koçulu is a software developer who was working on a personal project called
kik \cite{qz}. Coincidentally, Kik was also the name of a company in Ontario,
Canada \cite{qz, crunchbase}. The company reached out to Koçulu requesting that
he change the name of his project. Koçulu refused, and the company proceeded to
file a complaint with npm \cite{qz}. npm (following its Dispute Resolutinon
Policy \cite{npm-dispute-policy}) then decided to transfer the name kik to the
company, which caused Koçulu to remove all of his packages from the npm
registry, stating

@@

After an attempt to publish left-pad under a new version failed (due to some
major dependencies relying on the old version specificially, which was no longer
available), npm resulted to restoring the package from a backup
\cite{npmblog-leftpad}. The total downtime taken to restore the backup was 2.5
hours \cite{npmblog-leftpad}.

@@

npm ended up enacting two policies relating to unpublishing packages. The first
policy applied on packages that were less than 72 hours old, allowing
unpublishing as long as `no other packages in the npm Public Registry depend on
your package' \cite{npm-docs-unpublishing}.

The second policy applied to packages that were older than 72 hours, allowing
unpublishing as long as three conditions were met \cite{npm-docs-unpublishing}:
\begin{enumerate}
  \item no other packages in the npm Public Registry depend on it
  \item it had less than 300 downloads over the last week
  \item it has a single owner/maintainer
\end{enumerate}

@@

This was also caused by the fact that the `everything' package depended on a `*'
version of all of its packages, which meant that it matched any version of each
of its packages. Even if developers published a new version of their packages,
the `everything' package would actually just depend on both the old and new
versions of the package \cite{uncenter-blog-everything}.

@@

@@

\subsubsection{hoarders}
was a package created by Josh Holbrook that was created near the conception of
npm (2012) that also depended on 11,000 packages at its inception
\cite{github-hoarders-dependencies}. Isaac Schluter (the founder of npm) talked
with the creator of the package and convinced him to unpublish it
\cite{github-hoarders}.  A few years later in Aug 19, 2021, Josh Holbrook found
a way to work around having a heavy load on npm.

@@

\section{GitHub's Response}
Due to this happening over the holidays, it was only until the end of day on Jan
2, 2024 that GitHub reached out to the developers and notified them that they
were aware of the problem \cite{uncenter-blog-everything}. The next day (Jan
3rd), GitHub flagged the repository and began removing the packages on npm.

\subsection{Review}
On Jan 4th, GitHub sent a follow-up email to the developers classifying the
project as against their terms of service, and that they would be removing the
repository \cite{uncenter-blog-everything}. GitHub removed the repository and
packages from npm.

\section{Design Flaw Analysis}
The `everything' incident exposed a fundamental flaw: npm's design allows
developers to create packages that depend on every other package in the
registry, or a large number of packages.

@@

At its core, this is a fundamental design flaw of npm. The npm registry is
designed to be a public registry, and as such, it is difficult to prevent
developers from creating packages that depend on every other package in the
registry. This is a problem that is difficult to solve without fundamentally
changing the design of the npm registry.

\subsection{Other Potential Solutions}
\subsubsection{Rate Limiting}
One potential solution to this problem is to rate limit the number of packages
that a single package can depend on. This would prevent developers from creating
packages that depend on every other package in the registry.

@@

\subsubsection{Dependency Analysis}
Another potential solution is to analyze the dependencies of a package before
allowing it to be published. If a package depends on every other package in the
registry (or a significant portion of it), it could be flagged for review by the
npm team.

Static code analysis could additionally be used to detect dependencies that are
not actually used by the package, and flag the package for review.

@@

\appendix
\section{Appendix: Reading Resources}
\begin{itemize}
  \item Azer Koçulu himself wrote a blog post about the incident, which can be
        found at \cite{appendix-medium-azer}.
  \item The everything team created a website advertising the package, which can
        be found at \cite{appendix-everything-website}.
\end{itemize}

>>>>

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that
  allows developers to share javascript packages and libraries \cite{npm}. This
  article will review and analyze the design flaw of npm and how it was broken
  by a single package, and will also review how GitHub responded to the
  incident.
\end{abstract}

@@

The npm registry is a critical piece of infrastructure for the entire JavaScript
community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
that the npm registry will be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
incident in 2023 \cite{youtube-everything} has shown that the npm registry is
not as mature as developers had hoped.

\section{Historical Background}
\subsection{Introduction}
One of the most infamous events in the history of npm was the left-pad incident.
Azer Koçulu is a software developer who was working on a personal project called
kik \cite{qz}. Coincidentally, Kik is also the name of a company in Ontario,
Canada \cite{qz, crunchbase}. On March 11 2016, the company reached out to
Koçulu requesting that he change the name of his project. Koçulu refused, and
the company proceeded to file a complaint with npm \cite{qz}. npm (following its
Dispute Resolutinon Policy \cite{npm-dispute-policy}) decided to transfer the
name kik to the company. In response, Koçulu decided to remove all of his
packages from the npm registry, stating

@@

After an attempt to publish left-pad under a new version failed (due to some
dependencies relying on the older version specificially, which was no longer
available), npm resulted to restoring the package from a backup
\cite{npmblog-leftpad}. The total downtime taken to restore the backup was 2.5
hours \cite{npmblog-leftpad}.

@@

npm ended up enacting two policies relating to unpublishing packages. The first
policy applied on packages less than 72 hours old, allowing
unpublishing as long as `no other packages in the npm Public Registry depend on
your package' \cite{npm-docs-unpublishing}.

The second policy applied to packages older than 72 hours, allowing
unpublishing as long as three conditions were met \cite{npm-docs-unpublishing}:
\begin{enumerate}
  \item no other packages in the npm Public Registry depend on it
  \item it had less than 300 downloads over the last week
  \item it has a single owner/maintainer
\end{enumerate}

@@

A contributing factor to the incident was that the `everything' package was that
the `everything' package depended on a `*' version of all of its packages, which
meant that it matched any version of each of its packages. Even if developers
published a new version of their packages, the `everything' package would
actually just depend on both the old and new versions of the package
\cite{uncenter-blog-everything}.

@@

\subsubsection{hoarders}
was a package created by Josh Holbrook that was created near the conception of
npm (2012) that also depended on 11,000 packages at its inception
\cite{github-hoarders-dependencies}. Isaac Schlueter (the founder of npm) talked
with the creator of the package and convinced him to unpublish it to avoid
performance issues with npm \cite{github-hoarders}.  Nearly a decade later on
Aug 19, 2021, Josh Holbrook found a way to work around having a heavy impact on
npm.

@@

@@

\section{GitHub's Response}
Due to this happening over the holidays, it was only until the evening of Jan 2,
2024 that GitHub reached out to the developers and notified them that they were
aware of the problem \cite{uncenter-blog-everything}. The next day (Jan 3rd),
GitHub flagged the repository and began removing the packages on npm.

\subsection{Follow Up}
On Jan 4th, GitHub sent a follow-up email to the developers classifying the
project as against their terms of service, and that they would be removing the
repository \cite{uncenter-blog-everything}. GitHub removed the repository and
packages from npm the same day \cite{scmagazine-everything-blog}.

\section{Design Flaw Analysis}
The `everything' incident exposed a fundamental flaw: npm's handling of
unpublishing and dependencies was not as robust as it should have been. npm
had gone from one package being removed breaking many packages, to one package
being added preventing other packages from being removed.

@@

\subsection{Other Potential Solutions}
At its core, this is a fundamental design flaw of npm. The npm registry is
designed to be a public registry, and as such, it is difficult to reliably allow
developers to unpublish resources without impacting others. This is a problem
that is difficult to solve without fundamentally changing the design of the npm
registry.

\subsubsection{Rate Limiting}
One potential solution to this problem is to rate limit the number of packages
that a single package can depend on. This would prevent developers from creating
packages that depend on every other package in the registry.

@@

% \subsubsection{Dependency Analysis}
% Another potential solution is to analyze the dependencies of a package before
% allowing it to be published. If a package depends on every other package in the
% registry (or a significant portion of it), it could be flagged for review by the
% npm team.

% Static code analysis could additionally be used to detect dependencies that are
% not actually used by the package, and flag the package for review.

@@

\appendix
\section{Appendix: Reading Resources}
Azer Koçulu himself wrote a blog post about the incident, which can be found at
\cite{appendix-medium-azer}. \\
The everything team created a website advertising the package, which can be
found at \cite{appendix-everything-website}.
